\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2017-11-13 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
switched the license to GNU version 3 (now that we use pyCMT3D, which is LGPL v3, the combination automatically becomes GNU version 3). Also added FWI inversion information to the users manual.

@@

\title{\textbf{SPECFEM3D Cartesian}\\
 \textbf{User Manual}}

\author{\copyright Princeton University (USA), CNRS and University of Marseille (France),\\
and ETH Z\"urich (Switzerland)\\
Version 3.0}

@@

>>>>

% BibTeX logo
\newcommand{\BibTeX}{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em{T}\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\title{\textbf{SPECFEM3D}\\
\textbf{Cartesian}\\
 \textbf{User Manual}}

\author{\copyright \, CNRS (France), Princeton University (USA),\\
and ETH Z\"urich (Switzerland)\\
Version 3.0}

@@

\include{08b_performing_full_waveform_inversion_FWI_or_source_inversions}
